\documentclass{article}
\usepackage[english]{babel}
\title{Great deluge algorithm}

\begin{document}
\maketitle 
\section{Requirements}
The program was written and tested in Python2.5.\\
To visualize solution you need to install {\tt{}matplotlib} and {\tt{}numpy} module.

\section{Usage}

To call a program type:
\begin{verbatim}python  main.py [options]\end{verbatim}

Available options:

\begin{itemize}

\item{--action=}
\begin{verbatim}python main.py -a=action\end{verbatim}
Select the goal of run:
    \begin{itemize}
                \item{\tt{}c} All constructive heuristics.
                \item{\tt{}cgreedy} Greedy constructive heuristic.
                \item{\tt{}cpeckish} Peckish constructive heuristic.
                \item{\tt{}crandom} Random constructive heuristic.
                \item{\tt{}iterative} Iterative local search with random initialisation.
                \item{\tt{}deluge} Great deluge with default initialisation.
                \item{\tt{}delugeall} Run great deluge with peckish, random and greedy initialisation.
                \item{\tt{}delugerandom} Run great deluge with random initialisation.
                \item{\tt{}delugegreedy} Run great deluge with greedy initialisation.
                \item{\tt{}delugepeckish} Run great deluge with peckish initialisation.
    \end{itemize}
        
\item{--dataset=}
\begin{verbatim}python main.py -d=number\end{verbatim}
Select the set from input file to be used. If you type {\tt{}-d=*}, all sets are used instead.

\item{--help}
\begin{verbatim}python main.py -h\end{verbatim}
Print list of commands.

\item{--input=}
\begin{verbatim}python main.py -i=path\end{verbatim}
Path to input file. Default path is 'sets/gap1.txt'.

\item{--solution}
\begin{verbatim}python main.py -s\end{verbatim}
Print solution as table job:worker.

\item{--visualize}
\begin{verbatim}python main.py -v\end{verbatim}
Visualize solution.\\
Required modules: numpy, matplotlib

\item{--time}
\begin{verbatim}python main.py -t\end{verbatim}
Print time marks (start and end of run).

\item{--beautyoff}
\begin{verbatim}python main.py -b\end{verbatim}
Strip some decorative texts.

\end{itemize}

Examples:
\begin{verbatim}
python main.py -i="sets/gap9.txt" -s -t -d=* -a=delugerandom
python main.py -i="sets/gap9.txt" -t -v -a=delugerandom
\end{verbatim}

\section{Structure}
\begin{itemize}
    \item{main.py} Call other programmes and mark time.
    \item{local$\_{}$search.py} Implement great deluge and iterative search.
    \item{constructive$\_{}$heuristics.py} Implement constructive heuristics.
    \item{visualisation.py} Implement generating of 3d image using matplotlib and numpy.
    \item{process$\_{}$data.py} Load and process input.
    \item{img} Examples of visualization. Green color means good solution, more red in RGB means worse solution. 
\end{itemize}
\end{document}